Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-21 article.tex
Revert "Correction d'un bout de mise en page"
This reverts commit 6110e6c9fbb40ba0c6afd953317f3e0f3cc515c8.
Correction d'un bout de mise en page
Reprise mise en page du code

\section{Related works}

@@

\subsection{Additional database}
In order to compare the results of city detection, we needed a reference database. We therefore used the population data provided by INSEE.
[Pas sur de l'utilité de présenter cette base en fait, ptet juste la principale suffit]

@@

\subsection{Finding real neighbours}
For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
\subsubsection{Distance criterion\cite{patent_neighs}}
A \acrshort{bs} does not have an infinite coverage area.
As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.

@@

\section{Conclusion}

[Ouverture: prendre en compte les zazimuths]

>>>>

\section{Related works}
    \noindent

@@

    \subsection{Additional database}
        In order to compare the results of city detection, we needed a reference database. We therefore used the population data provided by INSEE.
        [Pas sûr de l'utilité de présenter cette base en fait, ptet juste la principale suffit]

@@

    \subsection{Finding real neighbours}
        For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
        As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
        \subsubsection{Distance criterion}
            A \acrshort{bs} does not have an infinite coverage area.
            As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.

@@

\section{Conclusion}
    [Ouverture: prendre en compte les zazimuths]
